### 2021-03-09 results/draft.tex
wrote the paragraph of Tokyo Bay

\ \ \ \ \ \ \ \ \ \
There are two straightforward approaches to resolving this issue. The first approach is DNA analysis. However, Egg samples are fixed with formalin to preserve their morphological characteristics and this results in DNA fragmentation and protein cross-linking, which makes DNA extraction difficult or impossible (e.g., Goelz et al., 1985; Impraim et al., 1987). The second approach is to use a mixture distribution of the eggs of chub mackerel and spotted mackerel which contains the temporal changes in egg diameters of two species. However, this is difficult on a practical level owing to complex and interconnected factors, such as spawning times within a given year, age, water temperature, and body condition affect egg diameter, and these may be difficult to obtain by field surveys alone (e.g., spawning times). As another solution, we modelled the species identification error by linking the catchability of egg density of spotted mackerel to the egg density of chub mackerel, because the recent increase of chub mackerel abundance may result in identification error for spotted mackerel egg. That is, an unexpected increase in the egg density of spotted mackerel is virtually replaced by the increase in catchability of the spotted mackerel eggs.

>>>>

\ \ \ \ \ \ \ \ \ \
Tokyo Bay is a large enclosed coastal sea in Japan. In Tokyo Bay, there are many useful species for fisheries that are colled "Edomae" because these species have been used for Sushi since Edo Era (about 400 years ago). Catch of some Edomae have been decreased because of habitat modification due to urbanization (e.g., landfill of tidal flats and water pollution). Catch statistics (total catch in each fish, efforts, and geographic location of fishing) have been collected for stock assessment since 1990 by prefectures around Tokyo Bay, which is widely collected and abundant.
In addition, scientific survey of eDNA has been conducted monthly in same points since 2018 for monitoring biodiveristy (Hongo et al., submitted).
